---
title: "Final Project - Wind Energy Forecasting"
output:
  html_document:
    df_print: paged
Group Member: Ealge Xuhui Ying, Susan Hang Yin, Jenny Shuhan Yue
---


## Load Libraries 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
options(warn = -1)
options(scipen = 999)
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(lubridate)
library(kableExtra)
library(GGally)
library(vip)        
library(fastshap)   
library(MASS)
library(ISLR)
library(tree)
library(ggplot2)
library(corrplot)
library(reshape2)
library(PerformanceAnalytics)
library(dplyr)
library(lubridate)
library(imputeTS)
library(forecast)
library(urca)
library(pracma)
library(astsa)
library(fpp2)

```

## Load Data

Import your data with read_csv()

```{r, eval=TRUE, warning=FALSE, message=FALSE}

row_data <- read_csv("Turbine_Data.csv") %>% clean_names()

row_data <- row_data %>% filter(year >= 2018)

head(row_data) 
tail(row_data)

```

## Missing values Interpolation

```{r, eval=TRUE, warning=FALSE, message=FALSE}

row_data$active_power <- na_interpolation(row_data$active_power)
row_data$ambient_temperature <- na_interpolation(row_data$ambient_temperature)
row_data$wind_direction <- na_interpolation(row_data$wind_direction)
row_data$wind_speed <- na_interpolation(row_data$wind_speed)

head(row_data)

```

## Time Index: Daily

Create a ts object for the aggregated data
Create a time plot of the aggregated data

```{r, eval=TRUE, warning=FALSE, message=FALSE}

turbine_data <- row_data %>%
  group_by(year, month, day) %>%
  summarize(active_power = sum(active_power), ambient_temperature = mean(ambient_temperature), wind_direction = mean(wind_direction), wind_speed = mean(wind_speed))

head(turbine_data)

```

## Explotary Analysis (scatterplot)

```{r, eval=TRUE, warning=FALSE, message=FALSE}
 turbine_data %>%
  ggplot(aes(x=ambient_temperature,y=active_power))+
  geom_point()

 turbine_data %>%
  ggplot(aes(x=wind_direction,y=active_power))+
  geom_point()

 turbine_data %>%
  ggplot(aes(x=wind_speed,y=active_power))+
  geom_point()

```

## Explotary Analysis (correlation)

```{r, eval=TRUE, warning=FALSE, message=FALSE}

cor <- turbine_data %>%
  ungroup() %>%
  na.omit() %>%
  dplyr::select(ambient_temperature, wind_direction, wind_speed)

chart.Correlation(cor,histogram=FALSE,pch=4)

cor_analysis <- cor %>%
  cor() %>%
  melt() %>% #turn it into a dataframe
  arrange(desc(value)) 

cor_analysis %>%
  ggplot(aes(x=Var1, y=Var2, fill=value))+
  geom_tile()+
  geom_text(aes(label=round(value,3)), color="white")

```

## Create time series object and plot time series

```{r, eval=TRUE, warning=FALSE, message=FALSE}

active_power_daily <- subset(turbine_data, select=c(active_power))
active_power_daily

# Create time series object and plot time series

active_power_ts <- ts(active_power_daily, start=c(2018,1,1), frequency = 365)
ts.plot(active_power_ts)

```

## Is this series white noise?

```{r, eval=TRUE, warning=FALSE, message=FALSE}

Box.test(active_power_ts, lag=8, fitdf=0, type="Lj")

```

## ADF test for stationarity
## Use the Single Mean Version of the Test

```{r, eval=TRUE, warning=FALSE, message=FALSE}

active_power_df <- ur.df(active_power_ts, type = "drift")
summary(active_power_df)

```

## Plot ACF and PACF
 
```{r, eval=TRUE, warning=FALSE, message=FALSE}

ggAcf(active_power_ts, lag = 200)

ggPacf(active_power_ts, lag = 200)

```

## Fit Seasonal Exponential Smoothing Model

```{r, eval=TRUE, warning=FALSE, message=FALSE}

active_power_ets <- ets(active_power_ts, model="ZNZ")
summary(active_power_ets)
checkresiduals(active_power_ets)
forecast(active_power_ts, h=5)
active_power_ets %>% forecast() %>% autoplot()

```

## Use auto.arima

```{r, eval=TRUE, warning=FALSE, message=FALSE}

fitauto <- auto.arima(active_power_ts)
summary(fitauto)
checkresiduals(fitauto)

fitauto %>% forecast(h=5)
fitauto %>% forecast() %>% autoplot()

```

## Which Explanatory Variables are Important?

```{r, eval=TRUE, warning=FALSE, message=FALSE}

fit1_AR0 <- sarima(active_power_ts, 0, 0, 0, xreg=turbine_data[,5:7])
summary(fit1_AR0)
fit1_AR0

```

## Explore AR(1,0,0)

```{r, eval=TRUE, warning=FALSE, message=FALSE}

fit1_AR1 <- sarima(active_power_ts, 1, 0, 0, xreg=turbine_data[,5:7])
summary(fit1_AR1)
fit1_AR1

```

## Remove Wind Direction

```{r, eval=TRUE, warning=FALSE, message=FALSE}

xreg2 <- subset(turbine_data, select=-c(wind_direction))

fit1_AR1 <- sarima(active_power_ts, 1, 0, 0, xreg=xreg2[,5:6])
summary(fit1_AR1)
fit1_AR1

```

## Remove Ambient Temperature

```{r, eval=TRUE, warning=FALSE, message=FALSE}

xreg3 <- subset(xreg2, select=-c(ambient_temperature))

fit1_AR1 <- sarima(active_power_ts, 1, 0, 0, xreg=xreg3[,5])
summary(fit1_AR1)
fit1_AR1

```

## Explore p, d, q Value

```{r, eval=TRUE, warning=FALSE, message=FALSE}

fit1_AR5 <- sarima(active_power_ts, 5, 0, 0, xreg=xreg3[,5])
summary(fit1_AR5)
fit1_AR5

reg_matrix <- as.matrix(xreg3[,5])
fit1_AR5 <- Arima(active_power_ts, order=c(5, 0, 0), xreg=reg_matrix)
summary(fit1_AR5)

fit1_AR5 %>% forecast(xreg=xreg3$wind_speed, h=5)

fit1_AR5 %>% forecast(xreg=xreg3$wind_speed, h=5) %>% autoplot()

```
## Use auto.arima

```{r, eval=TRUE, warning=FALSE, message=FALSE}

fit_auto <- auto.arima(active_power_ts, xreg=xreg3$wind_speed)
summary(fit_auto)
checkresiduals(fit_auto)

fit_auto %>% forecast(xreg=xreg3$wind_speed, h=5)

fit_auto %>% forecast(xreg=xreg3$wind_speed, h=5) %>% autoplot()

```
